A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add sifting algorithm intro

>>>>

To minimize the OBDD, a novel minimization algorithm was introduced by
Rudell~\cite{RUDELL93}, referred to as \textit{sifting algorithm}. It tries to
find the ideal position of one variable when all other variables keep their
positions. By definition, the ideal position of a variable is the position which
minimizes the size of the OBDD.
